\begin{thebibliography}{9}

\setlength{\itemsep}{1pt}

\bibitem{dubins} 
Dubins, L.E., 1957. On curves of minimal length with a constraint on average curvature, and with prescribed initial and terminal positions and tangents. American Journal of mathematics, 79(3), pp.497-516.

\bibitem{main_review}
Tan, C.S., Mohd-Mokhtar, R. and Arshad, M.R., 2021. A comprehensive review of coverage path planning in robotics using classical and heuristic algorithms. IEEE Access, 9, pp.119310-119342.

\bibitem{reeds}
Reeds, J. and Shepp, L., 1990. Optimal paths for a car that goes both forwards and backwards. Pacific journal of mathematics, 145(2), pp.367-393.

\bibitem{TSPN}
Dumitrescu, A. and Mitchell, J.S., 2003. Approximation algorithms for TSP with neighborhoods in the plane. Journal of Algorithms, 48(1), pp.135-159.

\bibitem{TSP_with_dubins}
Savla, K., Frazzoli, E. and Bullo, F., 2005, June. On the point-to-point and traveling salesperson problems for Dubins' vehicle. In Proceedings of the 2005, American Control Conference, 2005. (pp. 786-791). IEEE.

\bibitem{DTSPN}
Váňa, P. and Faigl, J., 2015, September. On the dubins traveling salesman problem with neighborhoods. In 2015 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS) (pp. 4029-4034). IEEE.

\bibitem{overlap}
Isaacs, J.T. and Hespanha, J.P., 2013. Dubins traveling salesman problem with neighborhoods: A graph-based approach. Algorithms, 6(1), pp.84-99.

\bibitem{mapping}
Choudhary, A., Kobayashi, Y., Arjonilla, F.J., Nagasaka, S. and Koike, M., 2021, January. Evaluation of mapping and path planning for non-holonomic mobile robot navigation in narrow pathway for agricultural application. In 2021 IEEE/SICE International Symposium on System Integration (SII) (pp. 17-22). IEEE.

\bibitem{random_walk}
Kegeleirs, M., Garzón Ramos, D. and Birattari, M., 2019, July. Random walk exploration for swarm mapping. In Annual conference towards autonomous robotic systems (pp. 211-222). Cham: Springer International Publishing.

\bibitem{dynamic_programming}
Zhou, P., Wang, Z.M., Li, Z.N. and Li, Y., 2012, September. Complete coverage path planning of mobile robot based on dynamic programming algorithm. In 2nd International Conference on Electronic \& Mechanical Engineering and Information Technology (pp. 1837-1841). Atlantis Press.

\bibitem{artificial_potential_field} 
Yan, J., Li, Y., Song, Z. and Zhang, Q., 2019. Research on UAV coverage path planning algorithm based on improved artificial potential field method. Oper. Res. Fuzziol., 9(4), pp.264-270.

\bibitem{spanning_tree} 
Gabriely, Y. and Rimon, E., 2001. Spanning-tree based coverage of continuous areas by a mobile robot. Annals of mathematics and artificial intelligence, 31, pp.77-98.

\bibitem{sampling_based} 
Lin, Y. and Saripalli, S., 2017. Sampling-based path planning for UAV collision avoidance. IEEE Transactions on Intelligent Transportation Systems, 18(11), pp.3179-3192.

\bibitem{sampling_based_more_related}
Karaman, S., 2012. Sampling-based algorithms for optimal path planning problems (Doctoral dissertation, Massachusetts Institute of Technology).

\bibitem{state_lattice}
Pivtoraiko, M., Knepper, R.A. and Kelly, A., 2007. Optimal, smooth, nonholonomic mobile robot motion planning in state lattices. Robotics Institute, Carnegie Mellon University, Pittsburgh, PA, Tech. Rep. CMU-RI-TR-07-15.

\bibitem{}
Galceran, E. and Carreras, M., 2013. A survey on coverage path planning for robotics. Robotics and Autonomous systems, 61(12), pp.1258-1276.

\bibitem{}
Muthukumaran, S., Ganesan, M., Dhanasekar, J. and Babu Loganathan, G., 2021. Path Planning Optimization for Agricultural Spraying Robots Using Hybrid Dragonfly–Cuckoo Search Algorithm. Alinteri Journal of Agriculture Sciences, 36(1), pp.2564-7814.

\bibitem{}
Gajjar, S., Bhadani, J., Dutta, P. and Rastogi, N., 2017, May. Complete coverage path planning algorithm for known 2d environment. In 2017 2nd IEEE International Conference on Recent Trends in Electronics, Information \& Communication Technology (RTEICT) (pp. 963-967). IEEE.

\bibitem{}
Kalaivanan, S. and Kalpana, R., 2017, June. Coverage path planning for an autonomous robot specific to agricultural operations. In 2017 International Conference on Intelligent Computing and Control (I2C2) (pp. 1-5). IEEE.

\bibitem{}
Victerpaul, P., Saravanan, D., Janakiraman, S. and Pradeep, J., 2017. Path planning of autonomous mobile robots: A survey and comparison. Journal of Advanced Research in Dynamical and Control Systems, 9(12), pp.1535-1565.

\bibitem{}
Zhao, S. and Hwang, S.H., 2024. Complete coverage path planning scheme for autonomous navigation ROS-based robots. ICT Express, 10(1), pp.83-89.

\bibitem{}
Sánchez-Ibáñez, J.R., Pérez-del-Pulgar, C.J. and García-Cerezo, A., 2021. Path planning for autonomous mobile robots: A review. Sensors, 21(23), p.7898.


\bibitem{}
Khan, A., Noreen, I. and Habib, Z., 2017. On Complete Coverage Path Planning Algorithms for Non-holonomic Mobile Robots: Survey and Challenges. J. Inf. Sci. Eng., 33(1), pp.101-121.

\bibitem{wow}  
Pěnička, R., Faigl, J., Váňa, P. and Saska, M., 2017, June. Dubins orienteering problem with neighborhoods. In 2017 International Conference on Unmanned Aircraft Systems (ICUAS) (pp. 1555-1562). IEEE.

\bibitem
Faigl, J. and Pěnička, R., 2017, September. On close enough orienteering problem with dubins vehicle. In 2017 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS) (pp. 5646-5652). IEEE.

\bibitem
Pěnička, R., Faigl, J., Váňa, P. and Saska, M., 2017. Dubins orienteering problem. IEEE Robotics and Automation Letters, 2(2), pp.1210-1217.

\bibitem
Drchal, J., Faigl, J. and Váňa, P., 2020. WiSM: Windowing surrogate model for evaluation of curvature-constrained tours with Dubins vehicle. IEEE Transactions on Cybernetics, 52(2), pp.1302-1311.

\bibitem
Vána, P. and Faigl, J., 2018, June. Optimal Solution of the Generalized Dubins Interval Problem. In Robotics: Science and Systems.

\bibitem
Faigl, J., Váňa, P., Saska, M., Báča, T. and Spurný, V., 2017, September. On solution of the Dubins touring problem. In 2017 European Conference on Mobile Robots (ECMR) (pp. 1-6). IEEE.

\bibitem
Faigl, J., Váňa, P. and Drchal, J., 2020, October. Fast sequence rejection for multi-goal planning with dubins vehicle. In 2020 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS) (pp. 6773-6780). IEEE.

\bibitem
Váňa, P. and Faigl, J., 2015. On sampling based methods for the dubins traveling salesman problem with neighborhoods.



\bibitem
Faigl, J., Váňa, P. and Deckerová, J., 2019. Fast heuristics for the 3-D multi-goal path planning based on the generalized traveling salesman problem with neighborhoods. IEEE Robotics and Automation Letters, 4(3), pp.2439-2446.




\bibitem
Kapoutsis, A.C., Chatzichristofis, S.A. and Kosmatopoulos, E.B., 2017. DARP: Divide areas algorithm for optimal multi-robot coverage path planning. Journal of Intelligent \& Robotic Systems, 86, pp.663-680.

\bibitem
Zafar, M.N. and Mohanta, J.C., 2018. Methodology for path planning and optimization of mobile robots: A review. Procedia computer science, 133, pp.141-152.

\bibitem
Pandey, A., Pandey, S. and Parhi, D.R., 2017. Mobile robot navigation and obstacle avoidance techniques: A review. Int Rob Auto J, 2(3), p.00022.

\bibitem
Chołodowicz, E. and Figurowski, D., 2017. Mobile robot path planning with obstacle avoidance using particle swarm optimization. Pomiary Automatyka Robotyka, 21(3), pp.59-68.

\bibitem
Islam, M.R., Protik, P., Das, S. and Boni, P.K., 2021. Mobile robot path planning with obstacle avoidance using chemical reaction optimization. Soft Computing, 25, pp.6283-6310.

\bibitem
Hameed, I.A., 2014. Intelligent coverage path planning for agricultural robots and autonomous machines on three-dimensional terrain. Journal of Intelligent \& Robotic Systems, 74(3), pp.965-983.

\bibitem
Selek, A., Seder, M., Brezak, M. and Petrović, I., 2022. Smooth complete coverage trajectory planning algorithm for a nonholonomic robot. Sensors, 22(23), p.9269.

\bibitem
Petereit, J., 2017. Adaptive State× Time Lattices: A contribution to mobile robot motion planning in unstructured dynamic environments (Vol. 27). KIT Scientific Publishing.

\bibitem
Choset, H., Lynch, K.M., Hutchinson, S., Kantor, G.A. and Burgard, W., 2005. Principles of robot motion: theory, algorithms, and implementations. MIT press.

\bibitem
Kalaivanan, S. and Kalpana, R., 2017, June. Coverage path planning for an autonomous robot specific to agricultural operations. In 2017 International Conference on Intelligent Computing and Control (I2C2) (pp. 1-5). IEEE.

\bibitem
Bormann, R., Jordan, F., Hampp, J. and Hägele, M., 2018, May. Indoor coverage path planning: Survey, implementation, analysis. In 2018 IEEE International Conference on Robotics and Automation (ICRA) (pp. 1718-1725). IEEE.

\bibitem
Pandey, A., Pandey, S. and Parhi, D.R., 2017. Mobile robot navigation and obstacle avoidance techniques: A review. Int Rob Auto J, 2(3), p.00022.

\bibitem
Kümpel, J., Sparbert, J., Tibken, B. and Hofer, E.P., 1999, August. Quadtree decomposition of configuration space for robot motion planning. In 1999 European Control Conference (ECC) (pp. 277-282). IEEE.



\bibitem
Dahiya, C. and Sangwan, S., 2018. Literature review on travelling salesman problem. International Journal of Research, 5(16), pp.1152-1155.

\bibitem
Yan, X., Zhang, C., Luo, W., Li, W., Chen, W. and Liu, H., 2012. Solve traveling salesman problem using particle swarm optimization algorithm. International Journal of Computer Science, 9(6), pp.264-271.

\bibitem
Raman, V. and Gill, N.S., 2017. Review of different heuristic algorithms for solving Travelling Salesman Problem. International Journal of Advanced Research in Computer Science, 8(5).

\bibitem
Váňa, P. and Faigl, J., 2020. Optimal solution of the Generalized Dubins Interval Problem: finding the shortest curvature-constrained path through a set of regions. Autonomous Robots, 44(7), pp.1359-1376.

\bibitem
Sankaranarayanan, A. and Vidyasagar, M., 1990, May. A new path planning algorithm for moving a point object amidst unknown obstacles in a plane. In Proceedings., IEEE International Conference on Robotics and Automation (pp. 1930-1936). IEEE.

\bibitem
Surynek, P., 2009, May. A novel approach to path planning for multiple robots in bi-connected graphs. In 2009 IEEE international conference on robotics and automation (pp. 3613-3619). IEEE.

\bibitem
Isaacs, J.T. and Hespanha, J.P., 2013. Dubins traveling salesman problem with neighborhoods: A graph-based approach. Algorithms, 6(1), pp.84-99.

\bibitem
Peng, C. and Isler, V., 2020. Visual coverage path planning for urban environments. IEEE Robotics and Automation Letters, 5(4), pp.5961-5968.

\bibitem
Viet, H.H., Dang, V.H., Laskar, M.N.U. and Chung, T., 2013. BA*: an online complete coverage algorithm for cleaning robots. Applied intelligence, 39, pp.217-235.

\bibitem
Hameed, I.A., 2017, July. Coverage path planning software for autonomous robotic lawn mower using dubins' curve. In 2017 IEEE International Conference on Real-time Computing and Robotics (RCAR) (pp. 517-522). IEEE.

\bibitem
Hameed, I.A., 2014. Intelligent coverage path planning for agricultural robots and autonomous machines on three-dimensional terrain. Journal of Intelligent \& Robotic Systems, 74(3), pp.965-983.

\bibitem
Zuo, G., Zhang, P. and Qiao, J., 2010, March. Path planning algorithm based on sub-region for agricultural robot. In 2010 2nd International Asia Conference on Informatics in Control, Automation and Robotics (CAR 2010) (Vol. 2, pp. 197-200). IEEE.

\bibitem
Barrientos, A., Colorado, J., Cerro, J.D., Martinez, A., Rossi, C., Sanz, D. and Valente, J., 2011. Aerial remote sensing in agriculture: A practical approach to area coverage and path planning for fleets of mini aerial robots. Journal of Field Robotics, 28(5), pp.667-689.

\bibitem
Hameed, I.A., Bochtis, D. and Sørensen, C.A., 2013. An optimized field coverage planning approach for navigation of agricultural robots in fields involving obstacle areas. International journal of advanced robotic systems, 10(5), p.231.

\bibitem
Zhou, K., Jensen, A.L., Sørensen, C.G., Busato, P. and Bothtis, D.D., 2014. Agricultural operations planning in fields with multiple obstacle areas. Computers and electronics in agriculture, 109, pp.12-22.

\bibitem
Sandamurthy, K. and Ramanujam, K., 2020. A hybrid weed optimized coverage path planning technique for autonomous harvesting in cashew orchards. Information Processing in Agriculture, 7(1), pp.152-164.

\end{thebibliography}